%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Name:        wxusedef.tex
%% Purpose:     wxUSE Preprocessor symbols
%% Author:      Tim Stahlhut
%% Created:     2007-07-15
%% RCS-ID:      $Id: $
%% Copyright:   (c) 2007 wxWidgets
%% License:     wxWindows license
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{wxUSE Preprocessor symbols defined by wxWidgets}\label{wxusedef}

These are wxUSE preprocessor symbols used in the wxWidgets source, grouped
by category (and sorted by alphabetical order inside each category). 
These symbols are always defined, if defined as $1$, feature is active.
So, they should be always tested using \texttt{#if} and not 
\texttt{#ifdef}.

\subsection{wxUSE preprocessor symbols use in more than one Platform}\label{wxusedefmulti}

\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_ABOUTDLG}{Use wxAboutDialogInfo class.}
\twocolitem{wxUSE\_ACCEL}{Use wxAcceleratorTable/Entry classes and support for them in wxMenu(Bar).}
\twocolitem{wxUSE\_ANIMATIONCTRL}{Use wxAnimationCtrl class.}
\twocolitem{wxUSE\_AUI}{Use wxWidget's AUI docking system.}
\twocolitem{wxUSE\_BASE}{only used by wxWidgets internally (defined as $1$ when
building wxBase code, either as a standalone library or as part of the
monolithic wxWidgets library, defined as $0$ when building GUI library only)}
\twocolitem{wxUSE\_BASE64}{Enables Base64 support.}
\twocolitem{wxUSE\_BITMAPCOMBOBOX}{}
\twocolitem{wxUSE\_BMPBUTTON}{Use wxBitmapButton class.}
\twocolitem{wxUSE\_BUSYINFO}{Use wxBusyInfo class.}
\twocolitem{wxUSE\_BUTTON}{Use wxButton class.}
\twocolitem{wxUSE\_CALENDARCTRL}{Use wxCalendarCtrl class.}
\twocolitem{wxUSE\_CARET}{Use wxCaret class.}
\twocolitem{wxUSE\_CHECKBOX}{Use wxCheckBox class.}
\twocolitem{wxUSE\_CHECKLISTBOX}{Use wxCheckListBox class.}
\twocolitem{wxUSE\_CHOICE}{Use wxChoice class.}
\twocolitem{wxUSE\_CHOICEBOOK}{Use wxChoicebook class.}
\twocolitem{wxUSE\_CHOICEDLG}{Use wxSingleChoiceDialog or wxMultiChoiceDialog classes.}
\twocolitem{wxUSE\_CLIPBOARD}{Use wxClipboard class.}
\twocolitem{wxUSE\_COLLPANE}{Use wxCollapsiblePane class.}
\twocolitem{wxUSE\_COLOURDLG}{Use wxColourDialog class.}
\twocolitem{wxUSE\_COLOURPICKERCTRL}{Use wxColourPickerCtrl class.}
\twocolitem{wxUSE\_COMBOBOX}{Use wxComboBox class.}
\twocolitem{wxUSE\_COMBOCTRL}{Use wxComboCtrl class.}
\twocolitem{wxUSE\_CONFIG}{Enables the use of wxConfig and related classes.}
\twocolitem{wxUSE\_CONSTRAINTS}{}
\twocolitem{wxUSE\_CONTROLS}{}
\twocolitem{wxUSE\_CRASHREPORT}{}
\twocolitem{wxUSE\_DATAOBJ}{Enables the use of wxDataObject and related classes.}
\twocolitem{wxUSE\_DATAVIEWCTRL}{Use wxDataViewCtrl class.}
\twocolitem{wxUSE\_DATEPICKCTRL}{Use wxDatePickerCtrl class.}
\twocolitem{wxUSE\_DATETIME}{Enables the use of wxDateTime and related classes.}
\twocolitem{wxUSE\_DEBUGREPORT}{Use wxDebugReport class.}
\twocolitem{wxUSE\_DIRDLG}{Use wxDirDialog class.}
\twocolitem{wxUSE\_DIRPICKERCTRL}{Use wxDirPickerCtrl class.}
\twocolitem{wxUSE\_DISPLAY}{Enables the use of wxDisplay and related classes.}
\twocolitem{wxUSE\_DOC\_VIEW\_ARCHITECTURE}{Enables the use of wxDocument and related classes.}
\twocolitem{wxUSE\_DRAGIMAGE}{Use wxDragImage class.}
\twocolitem{wxUSE\_EDITABLELISTBOX}{Use wxEditableListBox class.}
\twocolitem{wxUSE\_EXCEPTIONS}{}
\twocolitem{wxUSE\_FFILE}{Use wxFFile class.}
\twocolitem{wxUSE\_FILE}{Use wxFile class.}
\twocolitem{wxUSE\_FILEDLG}{Use wxFileDialog class.}
\twocolitem{wxUSE\_FILEPICKERCTRL}{Use wxFilePickerCtrl class.}
\twocolitem{wxUSE\_FILESYSTEM}{Enables the use of wxFileSystem and related classes.}
\twocolitem{wxUSE\_FINDREPLDLG}{Use wxFindReplaceDialog class.}
\twocolitem{wxUSE\_FONTDLG}{Use wxFontDialog class.}
\twocolitem{wxUSE\_FONTMAP}{Use wxFontMapper class.}
\twocolitem{wxUSE\_FONTPICKERCTRL}{Use wxFontPickerCtrl class.}
\twocolitem{wxUSE\_FSVOLUME}{Use wxFSVolumeBase class.}
\twocolitem{wxUSE\_GAUGE}{Use wxGauge class.}
\twocolitem{wxUSE\_GEOMETRY}{Use Common Geometry Classes}
\twocolitem{wxUSE\_GIF}{}
\twocolitem{wxUSE\_GLCANVAS}{Enables OpenGL support.}
\twocolitem{wxUSE\_GRID}{Enables the use of wxGrid and related classes.}
\twocolitem{wxUSE\_GUI}{this particular feature test macro is defined to $1$
when compiling or using the library with the GUI features activated, if it is
defined as $0$, only wxBase is available.}
\twocolitem{wxUSE\_HELP}{Enables the use of wxHelpController and related classes.}
\twocolitem{wxUSE\_HOTKEY}{}
\twocolitem{wxUSE\_HTML}{Enables the use of wxHtmlWindow and related classes.}
\twocolitem{wxUSE\_HYPERLINKCTRL}{}
\twocolitem{wxUSE\_IFF}{Enables the wxImage handler for Amiga IFF images.}
\twocolitem{wxUSE\_IMAGE}{Enables the use of wxImage and related classes.}
\twocolitem{wxUSE\_IMAGLIST}{Use wxImageList class.}
\twocolitem{wxUSE\_INTL}{Enables the use of wxLocale and related classes.}
\twocolitem{wxUSE\_IOSTREAMH}{Enables the use of header <iostream.h> instead of <iostream>.}
\twocolitem{wxUSE\_IPC}{Enables the use of Interprocess communication classes.}
\twocolitem{wxUSE\_JOYSTICK}{Use wxJoystick class.}
\twocolitem{wxUSE\_LIBJPEG}{Enables JPEG format support (requires libjpeg).}
\twocolitem{wxUSE\_LIBPNG}{Enables PNG format support (requires libpng). 
Also requires wxUSE\_ZLIB.}
\twocolitem{wxUSE\_LIBTIFF}{Enables TIFF format support (requires libtiff).}
\twocolitem{wxUSE\_LISTBOOK}{Use wxListbook class.}
\twocolitem{wxUSE\_LISTBOX}{Use wxListBox class.}
\twocolitem{wxUSE\_LISTCTRL}{Use wxListCtrl class.}
\twocolitem{wxUSE\_LOG}{Enables the use of wxLog and related classes.}
\twocolitem{wxUSE\_LOGGUI}{Use wxLogGui class.}
\twocolitem{wxUSE\_LOGWINDOW}{Use wxLogFrame class.}
\twocolitem{wxUSE\_LONGLONG}{Use wxLongLong class.}
\twocolitem{wxUSE\_MDI}{}
\twocolitem{wxUSE\_MDI\_ARCHITECTURE}{}
\twocolitem{wxUSE\_MEDIACTRL}{Use wxMediaCtrl.}
\twocolitem{wxUSE\_MENUS}{Enables the use of wxMenu and related classes.}
\twocolitem{wxUSE\_METAFILE}{Enables the use of wxMetaFile and related classes.}
\twocolitem{wxUSE\_MIMETYPE}{Use wxFileType class.}
\twocolitem{wxUSE\_MINIFRAME}{Use wxMiniFrame class.}
\twocolitem{wxUSE\_MOUSEWHEEL}{}
\twocolitem{wxUSE\_MSGDLG}{Use wxMessageOutput class.}
\twocolitem{wxUSE\_NOTEBOOK}{Enables the use of wxNotebook and related classes.}
\twocolitem{wxUSE\_NUMBERDLG}{Use wxNumberEntryDialog class.}
\twocolitem{wxUSE\_ODBC}{Use ODBC classes.}
\twocolitem{wxUSE\_ODCOMBOBOX}{Use wxOwnerDrawnComboBox class.}
\twocolitem{wxUSE\_OWNER\_DRAWN}{Enables the use of interface for owner-drawn GUI elements.}
\twocolitem{wxUSE\_PALETTE}{Enables the use of wxPalette and related classes.}
\twocolitem{wxUSE\_PCX}{Enables wxImage PCX handler.}
\twocolitem{wxUSE\_PNM}{Enables wxImage PNM handler.}
\twocolitem{wxUSE\_POPUPWIN}{Use wxPopupWindow class.}
\twocolitem{wxUSE\_POSTSCRIPT}{Use wxPostScriptPrinter class.}
\twocolitem{wxUSE\_PRINTING\_ARCHITECTURE}{Enable printer classes.}
\twocolitem{wxUSE\_PROGRESSDLG}{Enables progress dialog classes.}
\twocolitem{wxUSE\_PROTOCOL}{Use wxProtocol class.}
\twocolitem{wxUSE\_RADIOBOX}{Use wxRadioBox class.}
\twocolitem{wxUSE\_RADIOBTN}{Use wxRadioButton class.}
\twocolitem{wxUSE\_REGEX}{Use wxRegEx class.}
\twocolitem{wxUSE\_RICHEDIT}{}
\twocolitem{wxUSE\_RICHTEXT}{Use wxRichTextCtrl class.}
\twocolitem{wxUSE\_SASH}{Use wxSashWindow class.}
\twocolitem{wxUSE\_SCROLLBAR}{Use wxScrollBar class.}
\twocolitem{wxUSE\_SEARCHCTRL}{Use wxSearchCtrl class.}
\twocolitem{wxUSE\_SLIDER}{Use wxSlider class.}
\twocolitem{wxUSE\_SOCKETS}{Enables Network address classes.}
\twocolitem{wxUSE\_SOUND}{Use wxSound class.}
\twocolitem{wxUSE\_SPINBTN}{Use wxSpinButton class.}
\twocolitem{wxUSE\_SPINCTRL}{Use wxSpinCtrl class.}
\twocolitem{wxUSE\_SPLASH}{Use wxSplashScreen class.}
\twocolitem{wxUSE\_SPLINES}{}
\twocolitem{wxUSE\_SPLITTER}{Use wxSplitterWindow class.}
\twocolitem{wxUSE\_STACKWALKER}{Enables wxStackWalker and related classes.}
\twocolitem{wxUSE\_STATBMP}{Use wxStaticBitmap class.}
\twocolitem{wxUSE\_STATBOX}{Use wxStaticBox class.}
\twocolitem{wxUSE\_STATLINE}{Use wxStaticLine class.}
\twocolitem{wxUSE\_STATTEXT}{Use wxStaticText class.}
\twocolitem{wxUSE\_STATUSBAR}{Use wxStatusBar class.}
\twocolitem{wxUSE\_STC}{Enables the wxWidgets implementation of Scintilla.}
\twocolitem{wxUSE\_STDPATHS}{Use wxStandardPaths class.}
\twocolitem{wxUSE\_STL}{Use Standard Template Library.}
\twocolitem{wxUSE\_STOPWATCH}{Use wxStopWatch class.}
\twocolitem{wxUSE\_STREAMS}{Enable stream classes.}
\twocolitem{wxUSE\_SVG}{Use wxSVGFileDC class.}
\twocolitem{wxUSE\_TARSTREAM}{Enable Streams for Tar files.}
\twocolitem{wxUSE\_TEXTBUFFER}{Use wxTextBuffer class.}
\twocolitem{wxUSE\_TEXTCTRL}{Use wxTextCtrl class.}
\twocolitem{wxUSE\_TEXTDLG}{Use wxTextEntryDialog class.}
\twocolitem{wxUSE\_TEXTFILE}{Use wxTextFile class.}
\twocolitem{wxUSE\_TGA}{Enable wxImage TGA handler.}
\twocolitem{wxUSE\_THREADS}{Enables the use of wxThread and related classes.}
\twocolitem{wxUSE\_TIMER}{Use wxTimer class.}
\twocolitem{wxUSE\_TIPWINDOW}{Use wxTipWindow class.}
\twocolitem{wxUSE\_TOGGLEBTN}{Use wxToggleButton class.}
\twocolitem{wxUSE\_TOOLBAR}{Use wxToolBar class.}
\twocolitem{wxUSE\_TOOLBOOK}{Use wxToolbook class.}
\twocolitem{wxUSE\_TOOLTIPS}{Use wxToolTip class.}
\twocolitem{wxUSE\_TREEBOOK}{Use wxTreebook class.}
\twocolitem{wxUSE\_TREECTRL}{Use wxTreeCtrl class.}
\twocolitem{wxUSE\_UNICODE}{}
\twocolitem{wxUSE\_URL}{Use wxURL class.}
\twocolitem{wxUSE\_VALIDATORS}{Use wxValidator class.}
\twocolitem{wxUSE\_VARIANT}{Use wxVariant class.}
\twocolitem{wxUSE\_WIZARDDLG}{Use wxWizard class.}
\twocolitem{wxUSE\_WXDIB}{Use wxDIB class.}
\twocolitem{wxUSE\_XML}{Use XML parsing classes.}
\twocolitem{wxUSE\_XPM}{Enable XPM reader for wxImage and wxBitmap classes.}
\twocolitem{wxUSE\_XRC}{Use wxWidget's XRC XML-based resource system.}
\twocolitem{wxUSE\_ZIPSTREAM}{Enable Streams for Zip files.}                
\twocolitem{wxUSE\_ZLIB}{Enables compile wxZlibInput/OutputStream classes. 
Also required by wxUSE\_LIBPNG.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in Unix Platforms}\label{wxusedefunix}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_GSTREAMER}{Use GStreamer library.}
\twocolitem{wxUSE\_LIBMSPACK}{Use libmspack library.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in Mac Platforms}\label{wxusedefmac}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_WEBKIT}{Use wxWebKitCtrl class.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in wxMSW Platform}\label{wxusedefmsw}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_ACCESSIBILITY}{Use Library oleacc.lib}
\twocolitem{wxUSE\_ACTIVEX}{Enables the use of wxActiveXContainer and related classes.}
\twocolitem{wxUSE\_ENH\_METAFILE}{Enables the use of wxEnhMetaFile and related classes.}
\twocolitem{wxUSE\_INKEDIT}{}
\twocolitem{wxUSE\_MFC}{}
\twocolitem{wxUSE\_OLE}{Enables OLE helper routines.}
\twocolitem{wxUSE\_OLE\_AUTOMATION}{Enable OLE automation utilities.}
\twocolitem{wxUSE\_RICHEDIT2}{}
\twocolitem{wxUSE\_UXTHEME}{Enable support for XP themes.}
\twocolitem{wxUSE\_XPM\_IN\_MSW}{See also wxUSE\_XPM}
\end{twocollist}

 	  	 
